%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

\usepackage{amsmath}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-skyblue}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Paul}{Legler}
\position{Computer Science{\enskip\cdotp\enskip}Electrical Engineering}
\address{1411 23rd St., Manhattan Beach, CA 90266}

\mobile{310-200-7994}
\email{plegler24@gmail.com}
\homepage{paullegler.me}
\github{paullegler}
\linkedin{paul-legler}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Company Recruitment Team}
  {Handshake Inc.\\}
\letterdate{\today}
\lettertitle{Job Application for Backend Software Engineer--San Francisco}
\letteropening{Dear Company Recruiter,}
\letterclosing{Sincerely,}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Paul Legler~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
I am a senior majoring in Electrical Engineering and Computer Science at UC Berkeley. I particularly enjoyed courses in computer security and databases. Last semester, I was an undergraduate teaching assistant for the computer security course (CS 161) at Berkeley, and I enjoyed deepening my understanding of security and creating course curriculum. I am also president of Coaching Corps at UC Berkeley, which helps underserved youth in the bay area by providing student volunteer coaches. Outside of academics, I also enjoy playing and coaching basketball, dancing, and playing guitar.

Through my years at Berkeley and my four previous internships at Northrop Grumman, I have gained valuable experience that I am excited to demonstrate elsewhere. At Northrop Grumman, I have developed a number of tools aimed at increasing efficiency of other Northrop Grumman employees. For example, this summer I wrote a tool in Python and Visual Basic that provides predictions for important channel parameters like $\frac{\text{Carrier}}{\text{Noise}}$ ratio and $\frac{\text{Gain}}{\text{Temperature}}$ based on unit data, information in specification, and previous performance. Additionally, I rewrote some code that improved the modularity of encryption of data coming down from the spacecraft, which allowed for simpler decryption code, as well. As a teaching assistant, I was in charge of the second project, for which I rewrote in Go the staff solution and autograder alongside the professor. The improved autograder sped up the grading process exponentially.

I would love an opportunity to continue my growth a company with innovative ideas and a successful product I can work on. If you would like to set up an interview or send me a coding challenge, I would be excited to get to know your company better and for you to get to know me, as well!

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
